\documentclass{article}

\input{./style}

\title{\bfseries Operating DDOTI in Late 2020}
\author{Alan M. Watson}
\date{27 November 2020}

\begin{document}

\maketitle

\section{Safety}

We presume that the OAN will establish appropriate safety procedures for the COVID-19 pandemic.

The DDOTI team understand that the operations staff and the Secretario Técnico have complete authority to take decisions concerning safety. The safety guidelines for DDOTI are given in Chapter 2 of the manual.

\section{Communication}

\subsection{Operations Staff}

The operations staff will be Felipe Montalvo and Gustavo Melgoza.

%\begin{itemize}
%\item
%Ilse Plavchu
%\begin{itemize}
%\item Mobile/WhatsApp: +52-646-139-6164
%\item Email: ilse@astro.unam.mx
%\item Skype: ilseplauchufrayn
%\end{itemize}
%\item
%Carlos Guerrero
%\begin{itemize}
%\item Mobile/WhatsApp: 
%\item Email: cguerrero@astro.unam.mx
%\item Skype: cuadonte
%\end{itemize}
%\end{itemize}


\subsection{With the DDOTI Team}

The member of the DDOTI team with primary responsibility during the winter break is Alan Watson. Additional support will be provided by Diego González, William Lee, and Margarita Pereyra.

The primary communication channel with the DDOTI team will continue to be the existing “RATIR/COATLI/DDOTI” Skype chat group. All of the relevant persons are members of this chat and others can join if need be using:
\begin{quotation}
\url{https://join.skype.com/Ilxi4Wfm3ykB}
\end{quotation}
Team members monitor this chat from their computers and telephones.

In emergencies, team members can be contacted directly:

\begin{itemize}
\item
Diego González
\begin{itemize}
\item Mobile/WhatsApp: +52-646-276-3982
\item Email: dgonzalez@astro.unam.mx
\item Skype: dihegos
\end{itemize}
\item
William Lee
\begin{itemize}
\item Mobile/WhatsApp: +52:55-5504-7519
\item Email: wlee@astro.unam.mx
\item Skype: whleea
\end{itemize}
\item
Margarita Pereyra
\begin{itemize}
\item Mobile/WhatsApp: +52-646-117-2577
\item Email: mpereyra@astro.unam.mx
\item Skype: margarita-pereyra
\end{itemize}
\item
Alan Watson
\begin{itemize}
\item Mobile/WhatsApp: +52-55-3437-5003
\item Email: alan@astro.unam.mx
\item Skype: alan.watson.forster
\end{itemize}
\end{itemize}

\subsection{With the OAN}

\begin{itemize}
\item
OAN Coordinator on the mountain dial
\begin{itemize}
\item Landline: +52 (646) 175 0800 extension 593
\end{itemize}
\item
OAN Coordinator in Ensenada:
\begin{itemize}
\item Landline: +52 (646) 175 0800 extension 311
\end{itemize}
\item
Armando García Ruiz
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 102 9309
\end{itemize}
\item
Emanuel Mungarro García:
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 145 3840
\end{itemize}
\item
Esteban Valés Hernández:
\begin{itemize}
\item Mobile/WhatsApp:  +52 (646) 199 4889
\end{itemize}
\item Manuel Núñez Alfonso: 
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 131 7171 
\item Email: jnunez@astro.unam.mx 
\item Landline: +52 (646) 175 0800 extension 419
\end{itemize}
\end{itemize}

\section{Aims}

The aims for the operations staff are:

\begin{enumerate}

%\item
%To perform the Winter-Break Start-Up procedure according to \S3.6.2 of the Technical Manuals. This is necessary because the telescope is currently covered with a tarpaulin.
%
%Additionally, carry out a thorough inspection of the telescope, platform, enclosure, and shed, as these have not been closely inspected since March 2020.

\item
To perform daily operations of DDOTI according to \S3.3 of the Technical Manuals, with particular attention to the safety of personnel (first) and equipment (second). 

The safety guidelines are given in \S2 of the Technical Manuals.

If the operations staff have to close an enclosure locally (i.e., by physically going to the site rather than by using the control system web interface), operations of that telescope will be suspended unless and until explicitly authorized again by the Secretario Técnico.
\item
If necessary, perform the Winter-Break Shut-Down procedure for both telescopes according to \S3.6.1 of the Technical Manuals. 

%If the weather is good, we would recommend performing this operation on 23 December in order to facilitate leaving the mountain early on 24 December. If the weather forecast is poor for 23 December, this procedure can be carried out earlier.

%If conditions do not permit this procedure to be carried out safely, it can be omitted.

\item
To carry out minor maintenance (e.g., rebooting a computer) that does not require ascending to the platform.
\end{enumerate}

\section{Technical Manual}

The technical manual for DDOTI is available at:

\begin{quote}
%\url{http://coatli.astrossp.unam.mx/}\\
\url{http://ddoti.astrossp.unam.mx/}
\end{quote}

%However, these manuals are only accessible from the Instituto de Astronomía networks in CU, Ensenada, and SPM (either directly or by ssh tunnel).

%Furthermore, this site is currently down and is not expected to be up until later this week. For this reason, we will distribute a copy of chapters 2 and 3 or the manual by email.

\end{document}
