\documentclass{article}

\input{style}
\newcommand{\diego}[1]{{\color{red}{\textbf\small{#1}}}}

\title{\bfseries Operating COATLI and DDOTI in the Winter Break}
\author{Alan M. Watson}
\date{11 December 2019}

\begin{document}

\maketitle

\section{Communication}

\subsection{Operations Staff}

The operations staff during the winter break from 14 December to 24 December will be Ilse Plavchu and Rosa Becerra:

\begin{itemize}
\item
Ilse Plavchu
\begin{itemize}
\item Mobile/WhatsApp: +52-646-139-6164
\item Email: ilse@astro.unam.mx
\item Skype: ilseplauchufrayn
\end{itemize}
\item
Rosa Becerra
\begin{itemize}
\item Mobile/WhatsApp: +55-2311-6965
\item Email: rbecerra@astro.unam.mx
\item Skype: rosita\_miau
\end{itemize}
\end{itemize}


\subsection{With the COATLI/DDOTI Team}

The member of the COATLI/DDOTI team with primary responsibility during the winter break is Alan Watson. Additional support will be provided by Diego González, William Lee, and Margarita Pereyra.

The primary communication channel with the COATLI/DDOTI team will continue to be the existing “RATIR/COATLI/DDOTI” Skype chat group. All of the relevant persons are members of this chat and others can join if need be using:
\begin{quotation}
\url{https://join.skype.com/Ilxi4Wfm3ykB}
\end{quotation}
Team members monitor this chat from their computers and telephones.

In emergencies, team members can be contacted directly:

\begin{itemize}
\item
Diego González
\begin{itemize}
\item Mobile/WhatsApp: +52-646-276-3982
\item Email: dgonzalez@astro.unam.mx
\item Skype: dihegos
\end{itemize}
\item
William Lee
\begin{itemize}
\item Mobile/WhatsApp: +52:55-5504-7519
\item Email: wlee@astro.unam.mx
\item Skype: whleea
\end{itemize}
\item
Margarita Pereyra
\begin{itemize}
\item Mobile/WhatsApp: +52-646-117-2577
\item Email: mpereyra@astro.unam.mx
\item Skype: margarita-pereyra
\end{itemize}
\item
Alan Watson
\begin{itemize}
\item Mobile/WhatsApp: +52-55-3437-5003
\item Email: alan@astro.unam.mx
\item Skype: alan.watson.forster
\end{itemize}
\end{itemize}

\subsection{With the OAN}

\begin{itemize}
\item
OAN Coordinator on the mountain dial
\begin{itemize}
\item Landline: +52 (646) 175 0800 extension 593
\end{itemize}
\item
OAN Coordinator in Ensenada:
\begin{itemize}
\item Landline: +52 (646) 175 0800 extension 311
\end{itemize}
\item
Armando García Ruiz
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 102 9309
\end{itemize}
\item
Emanuel Mungarro García:
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 145 3840
\end{itemize}
\item
Esteban Valés Hernández:
\begin{itemize}
\item Mobile/WhatsApp:  +52 (646) 199 4889
\end{itemize}
\item Manuel Núñez Alfonso: 
\begin{itemize}
\item Mobile/WhatsApp: +52 (646) 131 7171 
\item Email: jnunez@astro.unam.mx 
\item Landline: +52 (646) 175 0800 extension 419
\end{itemize}
\end{itemize}

\section{Aims}

The aims for the operations staff are:

\begin{enumerate}

\item
To perform daily operations of COATLI and DDOTI according to \S3.3 of the Technical Manuals, with particular attention to the safety of personnel (first) and equipment (second). 

The safety guidelines are given in \S2 of the Technical Manuals.

If the operations staff have to close an enclosure locally (i.e., by physically going to the site rather than by using the control system web interface), operations of that telescope will be suspended unless and until explicitly authorized again by the Secretario Técnico.
\item
To perform the Winter-Break Shut-Down procedure for both telescopes according to \S3.6.1 of the Technical Manuals. 

If the weather is good, we would recommend performing this operation on 23 December in order to facilitate leaving the mountain early on 24 December. If the weather forecast is poor for 23 December, this procedure can be carried out earlier.

If conditions do not permit this procedure to be carried out safely, it can be omitted.
\item
To carry out minor maintenance (e.g., rebooting a computer) that does not require ascending to the platform.
\end{enumerate}

\section{Technical Manuals}

The technical manuals for DDOTI and COATLI are available at:

\begin{quote}
\url{http://coatli.astrossp.unam.mx/}\\
\url{http://ddoti.astrossp.unam.mx/}
\end{quote}

However, these manuals are only accessible from the Instituto de Astronomía networks in CU, Ensenada, and SPM (either directly or by ssh tunnel).

\end{document}
